|

### 2025-02-03 Drafts/Paper_1/01-analysis.Rmd

@@

```{r tunes}

@@

load(file = paste0(loc,"/Results/model_inputs_all_ages.Rdata"))

@@

   N.start <- all.abund[1]
   print(i)
   # The fecundities are 
   fast.for.tune <- fast.tunes(years,
                           tuner='fec_nm',
                           step.size = ss.size, 
                           abund.ts = all.abund,
                           ages=ages,
                           nm = -(log(1-prop.nat.mort)),
                           fecund = mx,
                           fm = fs,
                           abund.age = full.abund, 
                           catch.age = full.rem, 
                           N.init = N.start,
                           direction= 'forwards'
                           )

@@

#saveRDS(for.tune.summary,"D:/Github/ICM/Results/forwards_fully_tuned_summary_z.Rds")
#saveRDS(for.tune.all.res,"D:/Github/ICM/Results/forwards_fully_tuned_all_res_z.Rds")
# saveRDS(for.tune.summary,"D:/Github/ICM/Results/forwards_fully_tuned_summary_nm.Rds")
# saveRDS(for.tune.all.res,"D:/Github/ICM/Results/forwards_fully_tuned_all_res_nm.Rds")
#saveRDS(for.tune.summary,"D:/Github/ICM/Results/forwards_fully_tuned_summary_fm.Rds")
#saveRDS(for.tune.all.res,"D:/Github/ICM/Results/forwards_fully_tuned_all_res_fm.Rds")
saveRDS(for.tune.summary,"D:/Github/ICM/Results/forwards_fully_tuned_summary_fec_nm.Rds")
saveRDS(for.tune.all.res,"D:/Github/ICM/Results/forwards_fully_tuned_all_res_fec_nm.Rds")
#

@@

```{r paper-other-metrics-and-metadata}

# We are now looking at everything, lifetime reproductive success
model <- "fec_nm"
for.tune.summary <- readRDS(paste0("D:/Github/ICM/Results/forwards_fully_tuned_summary_",model,".Rds"))
for.tune.all <- readRDS(paste0("D:/Github/ICM/Results/forwards_fully_tuned_all_res_",model,".Rds"))

@@

meta$Area.broad[grep("GOM",meta$Area)] <- "GOM-GB"
meta$Area.long[grep("GOM",meta$Area)] <- "Gulf of Maine"
meta$Area.broad[grep("GB",meta$Area)] <- "GOM-GB"
meta$Area.long[grep("GB",meta$Area)] <- "Georges Bank"
meta$Area.broad[grep("5Y",meta$Area)] <- "GOM-GB"
meta$Area.long[grep("5Y",meta$Area)] <- "NAFO 5Y"
meta$Area.broad[grep("5Z",meta$Area)] <- "GOM-GB"
meta$Area.long[grep("5Z",meta$Area)] <- "NAFO 5Z"
meta$Area.broad[grep("USATL",meta$Area)] <- "GOM-GB" # The fishery is broader than just GOM, but it does also include it.
meta$Area.long[grep("USATL",meta$Area)] <- "US Atlantic" # The fishery is broader than just GOM, but it does also include it.
meta$Area.broad[grep("NWA",meta$Area)] <- "GOM-GB" # Mackerel... so that definition is a bit narrow....
meta$Area.long[grep("NWA",meta$Area)] <- "US Atlantic" # Mackerel... so that definition is a bit narrow....
#meta$Area1[grep("SNE- MA",meta$Area)] <- "GOM-GB" # YT in US, so no GB so that definition is a bit narrow....
meta$Area.broad[grep("MA",meta$Area)] <- "GOM-GB" # YT  and summer flounder in US, so no GB so that definition is a bit narrow....
meta$Area.long[grep("MA",meta$Area)] <- "Gulf of Maine" # YT  and summer flounder in US, so no GB so that definition is a bit narrow....
meta$Area.broad[grep("BSAI",meta$Area)] <- "BSAI"
meta$Area.broad[grep("4T",meta$Area)] <- "GSL"
meta$Area.long[grep("4T",meta$Area)] <- "NAFO 4T"
meta$Area.broad[grep("2J3",meta$Area)] <- "NFLD"
meta$Area.long[grep("2J3",meta$Area)] <- "NFLD"
meta$Area.broad[grep("3Pn-4RS",meta$Area)] <- "NFLD"
meta$Area.long[grep("3Pn-4RS",meta$Area)] <- "NFLD"
meta$Area.long[grep("GOA",meta$Area)] <- "Gulf of Alaska"
meta$Area.long[grep("AI",meta$Area)] <- "Aleutian Islands"
meta$Area.long[grep("ESB",meta$Area)] <- "Bering Sea"
meta$Area.long[grep("BSAI",meta$Area)] <- "Bering Sea & AI"
meta$Area[grep("BASI-Females",meta$Area)] <- "BSAI-Females"
meta$Area.long[grep("BSAI-Females",meta$Area)] <- "Bering Sea & AI"
meta$Area.narrow[meta$Stock == "ICES-NWWG_FA5b_Pollachius_virens"] <- "5b"
meta$Area.narrow[meta$Stock == "ICES-NWWG_FA5a_Pollachius_virens"] <- "5a"
meta$Area.narrow[meta$Stock == "ICES-WGNSSK_NS4 _Solea_solea"] <- "4"
meta$Area.narrow[meta$Stock == "ICES-WGNSSK_NS 7d._Solea_solea"] <- "7d"
meta$Area.narrow[meta$Stock == "ICES-WGBFAS_NS IIIa 22-24_Solea_Solea"] <- "22-24"
meta$Area.narrow[meta$Stock == "ICES-WGNSSK_NS 7d_Pleuronectes_platessa"] <- "7d"
meta$Area.narrow[meta$Stock == "ICES-WGNSSK_NS 4,20_Pleuronectes_platessa"] <- "4 20"
meta$Area.narrow[meta$Stock == "ICES-WGCSE_IS7e_Pleuronectes_platessa"] <- "7e"
meta$Area.narrow[meta$Stock == "ICES-WGCSE_IS27.7a_Pleuronectes_platessa"] <- "7a"
meta$Area.narrow[meta$Stock == "ICES-NWWG_FA5b_Melanogrammus_aeglefinus"] <- "5b"
meta$Area.narrow[meta$Stock == "ICES-NWWG_ICE5a_Melanogrammus_aeglefinus"] <- "5a"
meta$Area.narrow[meta$Stock == "ICES-WGBFAS_B28.1_Clupea_harengus"] <- "28"
meta$Area.narrow[meta$Stock == "ICES-WGBFAS_BS 25-29-32_Clupea_harengus" ] <- "25-32"
meta$Area.narrow[meta$Stock == "ICES-HAWG_WBS 22-24_Clupea_harengus"] <- "22-24"
meta$Area.narrow[meta$Stock == "DFO_4T-Fall_Clupea_harengus"] <- "Fall"
meta$Area.narrow[meta$Stock == "DFO_4T-Spring_Clupea_harengus"] <- "Spring"
meta$Area.narrow[meta$Stock == "ICES-WGCSE_CS27.6a_Merlangius_merlangus"] <- "27.6a"
meta$Area.narrow[meta$Stock == "ICES-WGCSE_CS7a_Merlangius_merlangus"] <- "7a"
meta$Area.narrow[meta$Stock == "ICES-NWWG_ICE5a_Gadus_morhua"] <- "5a"
meta$Area.narrow[meta$Stock == "ICES-NWWG_FAPL5b1_Gadus_morhua" ] <- "5b"
meta$Area.narrow[meta$Stock == "ICES-WGNSSK_NS 4-7d,20_Gadus_morhua"] <- "4-7 20"
meta$Area.narrow[meta$Stock == "ICES-WGCSE_NS6a_Gadus_morhua"] <- "6a"
meta$Area.narrow[meta$Stock == "DFO_2J3KL_Gadus_morhua"] <- "2J 3KL"
meta$Area.narrow[meta$Stock == "DFO_3Pn-4RS_Gadus_morhua"] <- "3Pn 4RS"
meta$Area.narrow[meta$Stock == "NEFSC-CERT-TRAC_GB _Gadus_morhua"] <- "East"

@@

# Do a years loop to get lambda with no fishing for each year, rather than by cohort...
  for(yy in 1:n.years)
  {
    nm <- as.numeric(tst$nm.opt[yy,])
    z <- as.numeric(tst$z.opt[yy,])
    fec <- as.numeric(tst$fecund.opt[yy,])
    nm.init <- as.numeric(tst$nm.org[yy,])
    fec.init <- as.numeric(tst$fecund.org[yy,])
    z.init <- as.numeric(tst$z.org[yy,])
    lam.no.fish <- exp(simple.lotka.r(Z = nm,fecund = fec,ages=ages)$res)
    lam.fish <- exp(simple.lotka.r(Z = z,fecund = fec,ages=ages)$res)
    lam.org.no.fish <- exp(simple.lotka.r(Z = nm.init,fecund = fec.init,ages=ages)$res)
    lam.org.fish <- exp(simple.lotka.r(Z =  z.init,fecund = fec.init,ages=ages)$res)

@@

dub.time.summary <- data.frame(dub.time.summary)
pop.dam <- data.frame(pop.dam)
# saveRDS(pop.dam,paste0("D:/Github/ICM/Results/R0_and_gen_length_",model,".Rds"))
# saveRDS(dub.time.summary,paste0("D:/Github/ICM/Results/doubling_time_",model,".Rds"))
# saveRDS(for.tunes,paste0("D:/Github/ICM/Results/forward_tunes_for_figures_",model,".Rds"))
save(dub.time.summary,pop.dam,res.year.final,res.cohort.final,for.tunes,dub.time,for.tune.all,res.lambda.final,meta,meta.sub,
     file=paste0("D:/Github/ICM/Results/all_cleaned_forward_tune_summaries_",model,".Rdata"))

write.csv(meta.sub, "D:/Github/ICM/Data/metadata.csv")

```{r simp-figs}
theme_set(theme_few(base_size = 14))
model <- 'fec_nm'
load(file=paste0("D:/Github/ICM/Results/all_cleaned_forward_tune_summaries_",model,".Rdata"))
pop.dam <- data.frame(pop.dam)
six.species <- c('morhua','harengus','aeglefinus','virens','solea','platessa')
pop.dam.6 <- pop.dam %>% dplyr::filter(Species %in% six.species)
for.tunes.6 <- for.tunes %>% dplyr::filter(Species %in% six.species)
dub.time.6 <- dub.time.summary %>% dplyr::filter(Species %in% six.species)
res.lambda.final$decade <- floor(res.lambda.final$year/10)*10
res.lambda.final <- res.lambda.final %>% dplyr::group_by(Stock,decade) %>% dplyr::mutate(mn.lam = mean(lam.fish,na.rm=T),
                                                                                 med.lam = median(lam.fish,na.rm=T),
                                                                                 sd.lam = sd(lam.fish,na.rm=T))
res.lambda.final <- res.lambda.final %>% dplyr::group_by(Species,decade) %>% dplyr::mutate(lm.spec.mn = mean(mn.lam,na.rm=T))              
res.lambda.final <- res.lambda.final %>% dplyr::group_by(Stock) %>% 
                                            dplyr::mutate(lam.no.fish.mn = mean(lam.no.fish,na.rm=T),
                                                          lam.fish.mn = mean(lam.fish,na.rm=T),
                                                          lam.org.no.fish.mn = mean(lam.org.no.fish,na.rm=T),
                                                          lam.org.fish.mn = mean(lam.org.fish,na.rm=T),
                                                          lam.no.fish.med = median(lam.no.fish,na.rm=T),
                                                          lam.fish.med = median(lam.fish,na.rm=T),
                                                          lam.org.no.fish.med = median(lam.org.no.fish,na.rm=T),
                                                          lam.org.fish.med = median(lam.org.fish,na.rm=T),) %>% data.frame()

@@

# Lambda plots

@@

save_plot("D:/Github/ICM/Figures/tuned/lambda_no_fishing_6.png",lambda.plt,base_width = 12,base_height = 10)

@@

save_plot("D:/Github/ICM/Figures/tuned/lambda_with_fishing_6.png",lambda.plt.fish,base_width = 12,base_height = 10)

@@

save_plot("D:/Github/ICM/Figures/tuned/Doubling_time_heatmap_by_sp6.png",dub.heatmap.sp6,base_width = 20,base_height = 17)

@@

save_plot("D:/Github/ICM/Figures/tuned/GL_boxplot_no_fish_6_species.png",gen.boxplt,base_width = 12,base_height = 10)

@@

save_plot("D:/Github/ICM/Figures/tuned/R0_boxplot_no_fish_6_species.png",r0.boxplt,base_width = 12,base_height = 10)

@@

save_plot("D:/Github/ICM/Figures/tuned/Doubling_time_heatmap_by_order.png",dub.heatmap,base_width = 20,base_height = 20)

@@

lambda.ts.plt <- ggplot(res.lambda.final.6,aes(y=lam.fish,x=year,group=Stock.short,color=Stock.short,shape = Stock.short,fill = Stock.short)) +
                            geom_point(size=4) +
                            geom_smooth(method='gam',formula = y ~ s(x, bs = "cs", fx = TRUE, k = 5),se=F) + 
                            #scale_y_log10(name = "lambda") +
                            facet_wrap(~G.Species,scales='free_y') +
                            scale_color_manual(name = "Stock",values = col.try) + scale_shape_manual(name = "Stock",values = pty) +
                            scale_fill_manual(name = "Stock",values = col.try)+
                            guides(colour = guide_legend(ncol = 1))+
                            theme(axis.text.x = element_text(angle =45,hjust=1),legend.key.width = unit(5,'cm'))
#lambda.ts.plt
save_plot("D:/Github/ICM/Figures/tuned/lambda_timeseries_6.png",lambda.ts.plt,base_width = 12,base_height = 10)

lambda.dec.plt <- ggplot(res.lambda.final.6,aes(y=med.lam,x=as.factor(decade))) +
                            geom_boxplot() + scale_y_log10()+
                            xlab("Decade") + ylab("Lambda") + 
                            geom_point(aes(x=as.factor(decade),y=lm.spec.mn),color='blue',shape=8,fill='blue')+
                            #scale_x_continuous(breaks=seq(1940,2020,by=10))+
                            geom_hline(yintercept = 1,linetype='dashed') +
                            facet_wrap(~G.Species,scales='free_y') 
save_plot("D:/Github/ICM/Figures/tuned/lambda_by_decade_6.png",lambda.dec.plt,base_width = 12,base_height = 12)

@@

save_plot("D:/Github/ICM/Figures/tuned/gen_heatmap.png",gen.heatmap,base_width = 20,base_height = 17)

@@

save_plot("D:/Github/ICM/Figures/tuned/r0_heatmap.png",r0.heatmap,base_width = 20,base_height = 17)

@@

# dub.heatmap.no.6 <- ggplot(dub.time.summary %>% dplyr::filter(!Species %in% six.species), aes(x=year, y=Stock.short, fill= prop)) + 
#                               xlab("") + ylab("")+                                    
#                               #facet_wrap(~G.Species,nrow=3,scales='free_y',strip.position = "right") + 
#                               scale_x_continuous() +
#                               geom_tile() + scale_fill_viridis(name = "Proportion",discrete=FALSE) + 
#                               theme(legend.position = 'none',text = element_text(size=12),plot.margin = margin(0,0.5,0,0.68, "cm"))

>>>>

  } # end load results
```

@@

```{r tunes,include=F,echo=F,warning=F,message=F}

@@

  if(load.results==F)
  {
  load(file = paste0(loc,"/Results/model_inputs_all_ages.Rdata"))

@@

     N.start <- all.abund[1]
     print(i)
     # The fecundities are 
     fast.for.tune <- fast.tunes(years,
                             tuner=what.2.tune,
                             step.size = ss.size, 
                             abund.ts = all.abund,
                             ages=0:max(ages),
                             nm = -(log(1-prop.nat.mort)),
                             fecund = mx,
                             fm = fs,
                             abund.age = full.abund, 
                             catch.age = full.rem, 
                             N.init = N.start,
                             direction= 'forwards'
                             )

@@

  #saveRDS(for.tune.summary,"D:/Github/ICM/Results/forwards_fully_tuned_summary_z.Rds")
  #saveRDS(for.tune.all.res,"D:/Github/ICM/Results/forwards_fully_tuned_all_res_z.Rds")
  # saveRDS(for.tune.summary,"D:/Github/ICM/Results/forwards_fully_tuned_summary_nm.Rds")
  # saveRDS(for.tune.all.res,"D:/Github/ICM/Results/forwards_fully_tuned_all_res_nm.Rds")
  #saveRDS(for.tune.summary,"D:/Github/ICM/Results/forwards_fully_tuned_summary_fm.Rds")
  #saveRDS(for.tune.all.res,"D:/Github/ICM/Results/forwards_fully_tuned_all_res_fm.Rds")
  saveRDS(for.tune.summary,paste0(loc,"/Results/forwards_fully_tuned_summary_",what.2.tune,".Rds"))
  saveRDS(for.tune.all.res,paste0(loc,"/Results/forwards_fully_tuned_all_res_",what.2.tune,".Rds"))
  # 
}# end if load results

@@

```{r paper-other-metrics-and-metadata,echo=F,include=F,warning=F,message=F}

if(load.results==F)
{
  # We are now looking at everything, lifetime reproductive success

  for.tune.summary <- readRDS(paste0(loc,"/Results/forwards_fully_tuned_summary_",what.2.tune,".Rds"))
  for.tune.all <- readRDS(paste0(loc,"/Results/forwards_fully_tuned_all_res_",what.2.tune,".Rds"))

@@

  meta$Area.broad[grep("GOM",meta$Area)] <- "GOM-GB"
  meta$Area.long[grep("GOM",meta$Area)] <- "Gulf of Maine"
  meta$Area.broad[grep("GB",meta$Area)] <- "GOM-GB"
  meta$Area.long[grep("GB",meta$Area)] <- "Georges Bank"
  meta$Area.broad[grep("5Y",meta$Area)] <- "GOM-GB"
  meta$Area.long[grep("5Y",meta$Area)] <- "NAFO 5Y"
  meta$Area.broad[grep("5Z",meta$Area)] <- "GOM-GB"
  meta$Area.long[grep("5Z",meta$Area)] <- "NAFO 5Z"
  meta$Area.broad[grep("USATL",meta$Area)] <- "GOM-GB" # The fishery is broader than just GOM, but it does also include it.
  meta$Area.long[grep("USATL",meta$Area)] <- "US Atlantic" # The fishery is broader than just GOM, but it does also include it.
  meta$Area.broad[grep("NWA",meta$Area)] <- "GOM-GB" # Mackerel... so that definition is a bit narrow....
  meta$Area.long[grep("NWA",meta$Area)] <- "US Atlantic" # Mackerel... so that definition is a bit narrow....
  #meta$Area1[grep("SNE- MA",meta$Area)] <- "GOM-GB" # YT in US, so no GB so that definition is a bit narrow....
  meta$Area.broad[grep("MA",meta$Area)] <- "GOM-GB" # YT  and summer flounder in US, so no GB so that definition is a bit narrow....
  meta$Area.long[grep("MA",meta$Area)] <- "Gulf of Maine" # YT  and summer flounder in US, so no GB so that definition is a bit narrow....
  meta$Area.broad[grep("BSAI",meta$Area)] <- "BSAI"
  meta$Area.broad[grep("4T",meta$Area)] <- "GSL"
  meta$Area.long[grep("4T",meta$Area)] <- "NAFO 4T"
  meta$Area.broad[grep("2J3",meta$Area)] <- "NFLD"
  meta$Area.long[grep("2J3",meta$Area)] <- "NFLD"
  meta$Area.broad[grep("3Pn-4RS",meta$Area)] <- "NFLD"
  meta$Area.long[grep("3Pn-4RS",meta$Area)] <- "NFLD"
  meta$Area.long[grep("GOA",meta$Area)] <- "Gulf of Alaska"
  meta$Area.long[grep("AI",meta$Area)] <- "Aleutian Islands"
  meta$Area.long[grep("ESB",meta$Area)] <- "Bering Sea"
  meta$Area.long[grep("BSAI",meta$Area)] <- "Bering Sea & AI"
  meta$Area[grep("BASI-Females",meta$Area)] <- "BSAI-Females"
  meta$Area.long[grep("BSAI-Females",meta$Area)] <- "Bering Sea & AI"
  meta$Area.narrow[meta$Stock == "ICES-NWWG_FA5b_Pollachius_virens"] <- "5b"
  meta$Area.narrow[meta$Stock == "ICES-NWWG_FA5a_Pollachius_virens"] <- "5a"
  meta$Area.narrow[meta$Stock == "ICES-WGNSSK_NS4 _Solea_solea"] <- "4"
  meta$Area.narrow[meta$Stock == "ICES-WGNSSK_NS 7d._Solea_solea"] <- "7d"
  meta$Area.narrow[meta$Stock == "ICES-WGBFAS_NS IIIa 22-24_Solea_Solea"] <- "22-24"
  meta$Area.narrow[meta$Stock == "ICES-WGNSSK_NS 7d_Pleuronectes_platessa"] <- "7d"
  meta$Area.narrow[meta$Stock == "ICES-WGNSSK_NS 4,20_Pleuronectes_platessa"] <- "4 20"
  meta$Area.narrow[meta$Stock == "ICES-WGCSE_IS7e_Pleuronectes_platessa"] <- "7e"
  meta$Area.narrow[meta$Stock == "ICES-WGCSE_IS27.7a_Pleuronectes_platessa"] <- "7a"
  meta$Area.narrow[meta$Stock == "ICES-NWWG_FA5b_Melanogrammus_aeglefinus"] <- "5b"
  meta$Area.narrow[meta$Stock == "ICES-NWWG_ICE5a_Melanogrammus_aeglefinus"] <- "5a"
  meta$Area.narrow[meta$Stock == "ICES-WGBFAS_B28.1_Clupea_harengus"] <- "28"
  meta$Area.narrow[meta$Stock == "ICES-WGBFAS_BS 25-29-32_Clupea_harengus" ] <- "25-32"
  meta$Area.narrow[meta$Stock == "ICES-HAWG_WBS 22-24_Clupea_harengus"] <- "22-24"
  meta$Area.narrow[meta$Stock == "DFO_4T-Fall_Clupea_harengus"] <- "Fall"
  meta$Area.narrow[meta$Stock == "DFO_4T-Spring_Clupea_harengus"] <- "Spring"
  meta$Area.narrow[meta$Stock == "ICES-WGCSE_CS27.6a_Merlangius_merlangus"] <- "27.6a"
  meta$Area.narrow[meta$Stock == "ICES-WGCSE_CS7a_Merlangius_merlangus"] <- "7a"
  meta$Area.narrow[meta$Stock == "ICES-NWWG_ICE5a_Gadus_morhua"] <- "5a"
  meta$Area.narrow[meta$Stock == "ICES-NWWG_FAPL5b1_Gadus_morhua" ] <- "5b"
  meta$Area.narrow[meta$Stock == "ICES-WGNSSK_NS 4-7d,20_Gadus_morhua"] <- "4-7 20"
  meta$Area.narrow[meta$Stock == "ICES-WGCSE_NS6a_Gadus_morhua"] <- "6a"
  meta$Area.narrow[meta$Stock == "DFO_2J3KL_Gadus_morhua"] <- "2J 3KL"
  meta$Area.narrow[meta$Stock == "DFO_3Pn-4RS_Gadus_morhua"] <- "3Pn 4RS"
  meta$Area.narrow[meta$Stock == "NEFSC-CERT-TRAC_GB _Gadus_morhua"] <- "East"

@@

  # Do a years loop to get lambda with no fishing for each year, rather than by cohort...
    for(yy in 1:n.years)
    {
      nm <- as.numeric(tst$nm.opt[yy,])
      z <- as.numeric(tst$z.opt[yy,])
      fec <- as.numeric(tst$fecund.opt[yy,])
      nm.init <- as.numeric(tst$nm.org[yy,])
      fec.init <- as.numeric(tst$fecund.org[yy,])
      z.init <- as.numeric(tst$z.org[yy,])
      lam.no.fish <- exp(simple.lotka.r(mort = nm,fecund = fec,ages=ages)$res$r)
      lam.fish <- exp(simple.lotka.r(mort = z,fecund = fec,ages=ages)$res$r)
      lam.org.no.fish <- exp(simple.lotka.r(mort = nm.init,fecund = fec.init,ages=ages)$res$r)
      lam.org.fish <- exp(simple.lotka.r(mort =  z.init,fecund = fec.init,ages=ages)$res$r)

@@

  dub.time.summary <- data.frame(dub.time.summary)
  pop.dam <- data.frame(pop.dam)
  # saveRDS(pop.dam,paste0("D:/Github/ICM/Results/R0_and_gen_length_",what.2.tune,".Rds"))
  # saveRDS(dub.time.summary,paste0("D:/Github/ICM/Results/doubling_time_",what.2.tune,".Rds"))
  # saveRDS(for.tunes,paste0("D:/Github/ICM/Results/forward_tunes_for_figures_",what.2.tune,".Rds"))
  save(dub.time.summary,pop.dam,res.year.final,res.cohort.final,for.tunes,dub.time,for.tune.all,res.lambda.final,meta,meta.sub,
       file=paste0(loc,"/Results/all_cleaned_forward_tune_summaries_",what.2.tune,".Rdata"))

  write.csv(meta.sub, paste0(loc,"/Data/metadata.csv"))
} # end if load results
```

```{r simp-figs,include=F,echo=F,message=F,warning=F}
load(file=paste0(loc,"/Results/all_cleaned_forward_tune_summaries_",what.2.tune,".Rdata"))
pop.dam <- data.frame(pop.dam)
six.species <- c('morhua','harengus','aeglefinus','virens','solea','platessa')
pop.dam.6 <- pop.dam %>% dplyr::filter(Species %in% six.species)
for.tunes.6 <- for.tunes %>% dplyr::filter(Species %in% six.species)
dub.time.6 <- dub.time.summary %>% dplyr::filter(Species %in% six.species)
res.lambda.final$decade <- floor(res.lambda.final$year/10)*10
res.lambda.final <- res.lambda.final %>% dplyr::group_by(Stock,decade) %>% dplyr::mutate(mn.lam = mean(lam.fish,na.rm=T),
                                                                                 med.lam = median(lam.fish,na.rm=T),
                                                                                 sd.lam = sd(lam.fish,na.rm=T))
res.lambda.final <- res.lambda.final %>% dplyr::group_by(Species,decade) %>% dplyr::mutate(lm.spec.mn = mean(mn.lam,na.rm=T))              
res.lambda.final <- res.lambda.final %>% dplyr::group_by(Stock) %>% 
                                            dplyr::mutate(lam.no.fish.mn = mean(lam.no.fish,na.rm=T),
                                                          lam.fish.mn = mean(lam.fish,na.rm=T),
                                                          lam.org.no.fish.mn = mean(lam.org.no.fish,na.rm=T),
                                                          lam.org.fish.mn = mean(lam.org.fish,na.rm=T),
                                                          lam.no.fish.med = median(lam.no.fish,na.rm=T),
                                                          lam.fish.med = median(lam.fish,na.rm=T),
                                                          lam.org.no.fish.med = median(lam.org.no.fish,na.rm=T),
                                                          lam.org.fish.med = median(lam.org.fish,na.rm=T),) %>% data.frame()

@@

@@

save_plot(paste0(loc,"/Figures/tuned/lambda_no_fishing_6_",what.2.tune,".png"),lambda.plt,base_width = 12,base_height = 10)

@@

save_plot(paste0(loc,"/Figures/tuned/lambda_with_fishing_6_",what.2.tune,".png"),lambda.plt.fish,base_width = 12,base_height = 10)

@@

save_plot(paste0(loc,"/Figures/tuned/Doubling_time_heatmap_by_sp6_",what.2.tune,".png"),dub.heatmap.sp6,base_width = 20,base_height = 17)

@@

save_plot(paste0(loc,"/Figures/tuned/GL_boxplot_no_fish_6_species_",what.2.tune,".png"),gen.boxplt,base_width = 12,base_height = 10)

@@

save_plot(paste0(loc,"/Figures/tuned/R0_boxplot_no_fish_6_species_",what.2.tune,".png"),r0.boxplt,base_width = 12,base_height = 10)

@@

save_plot(paste0(loc,"/Figures/tuned/Doubling_time_heatmap_by_order_",what.2.tune,".png"),dub.heatmap,base_width = 20,base_height = 20)

@@

lambda.ts.plt <- ggplot(res.lambda.final.6,aes(y=lam.fish,x=year,group=Stock.short,color=Stock.short,shape = Stock.short,fill = Stock.short)) +
                            geom_point(size=4) +
                            geom_smooth(method='gam',formula = y ~ s(x, bs = "cs", fx = TRUE, k = 5),se=F) + 
                            #scale_y_log10(name = "lambda") +
                            facet_wrap(~G.Species,scales='free_y') +
                            scale_color_manual(name = "Stock",values = col.try) + scale_shape_manual(name = "Stock",values = pty) +
                            scale_fill_manual(name = "Stock",values = col.try)+
                            guides(colour = guide_legend(ncol = 1))+
                            theme(axis.text.x = element_text(angle =45,hjust=1),legend.key.width = unit(5,'cm'))
#lambda.ts.plt
save_plot(paste0(loc,"/Figures/tuned/lambda_timeseries_6_",what.2.tune,".png"),lambda.ts.plt,base_width = 12,base_height = 10)

lambda.dec.plt <- ggplot(res.lambda.final.6,aes(y=med.lam,x=as.factor(decade))) +
                            geom_boxplot() + scale_y_log10()+
                            xlab("Decade") + ylab("Lambda") + 
                            geom_point(aes(x=as.factor(decade),y=lm.spec.mn),color='blue',shape=8,fill='blue')+
                            #scale_x_continuous(breaks=seq(1940,2020,by=10))+
                            geom_hline(yintercept = 1,linetype='dashed') +
                            facet_wrap(~G.Species,scales='free_y') 
save_plot(paste0(loc,"/Figures/tuned/lambda_by_decade_6_",what.2.tune,".png"),lambda.dec.plt,base_width = 12,base_height = 12)

@@

save_plot(paste0(loc,"/Figures/tuned/gen_heatmap_",what.2.tune,".png"),gen.heatmap,base_width = 20,base_height = 17)

@@

save_plot(paste0(loc,"/Figures/tuned/r0_heatmap_",what.2.tune,".png"),r0.heatmap,base_width = 20,base_height = 17)

@@

# dub.heatmap.no.6 <- ggplot(dub.time.summary %>% dplyr::filter(!Species %in% six.species), aes(x=year, y=Stock.short, fill= prop)) + 
#                               xlab("") + ylab("")+                                    
#                               #facet_wrap(~G.Species,nrow=3,scales='free_y',strip.position = "right") + 
#                               scale_x_continuous() +
#                               geom_tile() + scale_fill_viridis(name = "Proportion",discrete=FALSE) + 
#                               theme(legend.position = 'none',text = element_text(size=12),plot.margin = margin(0,0.5,0,0.68, "cm"))
```
